Education Analysis of the United States

### 2023-03-16 outputs/paper/paper.qmd
Update paper.qmd
Capitalized > 4 years of college category in the plot.

## Respondent
clean_data_respondent <-
  clean_data_respondent %>%
  mutate(
    education = fct_relevel(
      education,
      "< High School",
      "High School",
      "Some College",
      "4 Years of College",
      "> 4 years of college"
    )
  )

## Mom
clean_data_mom <-
  clean_data_mom %>%
  mutate(
    education = fct_relevel(
      education,
      "< High School",
      "High School",
      "Some College",
      "4 Years of College",
      "> 4 years of college"
    )
  )

## Dad
clean_data_dad <-
  clean_data_dad %>%
  mutate(
    education = fct_relevel(
      education,
      "< High School",
      "High School",
      "Some College",
      "4 Years of College",
      "> 4 years of college"
    )
  )

>>>>

## Respondent
clean_data_respondent <-
  clean_data_respondent %>%
  mutate(
    education = fct_relevel(
      education,
      "< High School",
      "High School",
      "Some College",
      "4 Years of College",
      "> 4 Years of College"
    )
  )

## Mom
clean_data_mom <-
  clean_data_mom %>%
  mutate(
    education = fct_relevel(
      education,
      "< High School",
      "High School",
      "Some College",
      "4 Years of College",
      "> 4 Years of College"
    )
  )

## Dad
clean_data_dad <-
  clean_data_dad %>%
  mutate(
    education = fct_relevel(
      education,
      "< High School",
      "High School",
      "Some College",
      "4 Years of College",
      "> 4 Years of College"
    )
  )
